WordRec Experiment

### 2018-11-26 Data_and_analysis/revisons1_pilot.Rmd
increase threshold for selection
sample size

#Skip the pre task trials 
#Filter subjects who had no technical problem
#Select subjects who got more than 50% correct answers on the pre task trials

@@

exp1_good <- exp1_noProb %>%
  filter(score > 0.5)

>>>>

##We will collect N=50 participants, and the data will be processed as follows

@@

exp1_good <- exp1_noProb %>%
  filter(score >= 0.75)
